%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage{tikz}

\newcommand{\ExternalLink}{%
    \tikz[x=1.2ex, y=1.2ex, baseline=-0.05ex]{%
        \begin{scope}[x=1ex, y=1ex]
            \clip (-0.1,-0.1)
                --++ (-0, 1.2)
                --++ (0.6, 0)
                --++ (0, -0.6)
                --++ (0.6, 0)
                --++ (0, -1);
            \path[draw,
                line width = 0.5,
                rounded corners=0.5]
                (0,0) rectangle (1,1);
        \end{scope}
        \path[draw, line width = 0.5] (0.5, 0.5)
            -- (1, 1);
        \path[draw, line width = 0.5] (0.6, 1)
            -- (1, 1) -- (1, 0.6);
        }
    }
%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}
% \usepackage[default]{arial}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-7pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItemWithHeading}[2]{
  \item{
    \textbf{#1}
    {#2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItem}[1]{
  \item{
    {#1 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      % \textit{\small#3} & \textit{\small #4} \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \small{#2} \\
      % {#3} & \textit{#4} \\
      % \textit{\small#3} & \textit{\small #4} \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeItemTwoFields}[2]{
  \item{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubItem}[2]{\resumeItemTwoFields{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://mathsforgeeks.org}{\Large Sidharrth Nagappan}} & Email : \href{mailto:sidharrth2002@gmail.com}{sidharrth2002@gmail.com}\\
  \href{https://mathsforgeeks.org}{https://mathsforgeeks.org/} | \href{https://github.com/sidharrth2002}{https://github.com/sidharrth2002} & Mobile : +60163132154 \\
\end{tabular*}

% \section{Research Interests}
% Deep Learning, Natural Language Processing, Computational Linguistics, Multimodal Learning, Low-resource Machine Learning, Computer Vision

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Bachelor of Computer Science (Hons.) in Data Science}{Cyberjaya, MY}
      {Multimedia University}{Nov 2018 - June 2023 (Expected)}
      \resumeItemListStart
        \resumeItem{\textbf{Current Undergraduate CGPA: 3.99/4.00 (Expected 1st Class Honours)}}
        \resumeItem{\textbf{Foundation Year CGPA: 4.00/4.00}- Top of cohort}
        \resumeItem{Distinction in Industrial Deep NLP thesis (Document Scoring Using Natural Language Processing) supervised by Ts. Dr. Goh Hui Ngo}
        \resumeItemTwoFields{Community Lead @ Google Developer Student Clubs}{Organised hackathons, arranged talks and taught workshops on Python, Javascript, Machine Learning, Git and Flutter with a cumulative total of 1000 participants. Was actively involved in the Google Developer Space (GDG) within KL and the greater Malaysian community.}
        \resumeItemTwoFields{President @ Hackerspace MMU}{Cyberjaya's largest hacker-maker group that promotes an engineering culture within the wider student developer community, in operation for over 10 years.}
      \resumeItemListEnd

      \resumeSubheading
      {Bachelor of Engineering (Computer Engineering)}{Turin, Italy}
      {Politecnico di Torino}{Sep 2022 - Feb 2023}
      \resumeItemListStart
        \resumeItem{Erasmus Exchange semester (22 ECTS completed with 12 from the masters level).}
        \resumeItem{Computational Intelligence- Evolutionary computation, swarm optimisation, genetic algorithms and reinforcement learning, taught at the masters level. Finished with 30L/30 distinction}
        \resumeItem{Human Computer Interaction- Advanced design patterns and human-centered software engineering taught at the masters level. Finished with 30L/30 distinction}
        \resumeItem{Mathematical Analysis II- Passed outside my major (engineering), where I learned about Laplace transforms, multiple integration, numerical series (Fourier), elementary notions of topology, conservative vector fields, fundamental electrical engineering and complex analysis. Only 33\% of all students passed the final examination in the first 2023 academic session.}
      \resumeItemListEnd

      \resumeSubheading
      {Cambridge International General Certificate of Secondary Education (IGCSE)}{Cyberjaya, MY}
      {elc International School}{July 2016 - July 2018}
      \resumeItemListStart
        \resumeItem{\textbf{9A*s} for 9 subjects- Mathematics, Additional Mathematics, First Language English, Biology, Chemistry, Physics, History, Business Studies and Malay}
        \resumeItem{Cambridge International Certificate in Education (ICE) with Distinction}
        \resumeItem{1st Rank- Graduated at the top of the class, Senior Prefect}
      \resumeItemListEnd
    \resumeSubHeadingListEnd

\section{Publications}
  \resumeItemListStart
  \resumeItem{\textbf{Sidharrth Nagappan*}, Jia Qi Tan*, Lai-Kuan Wong, John See. Context-Aware Multi-Stream Networks for Dimensional Emotion Prediction in Images \textit{In Proceedings of The 30th International Conference on Image Processing}, 2023.}
  \resumeItem{\textbf{Sidharrth Nagappan*}, Hui-Ngo Goh, Amy Hui-Lan Lim. Hybrid Deep Neural Networks for Industrial Text Scoring \textit{In Proceedings of The 35th International Conference on Industrial, Engineering \& Other Applications of Applied Intelligent Systems, Kitakyushu, Japan}, 2022.}
  \resumeItemListEnd
  \vspace{-10pt}

%-----------EXPERIENCE-----------------s
\section{Experience}
  \resumeSubHeadingListStart

  \resumeSubheading
  {Monash University Malaysia}{Petaling Jaya, Malaysia}
  {\textit{Sessional Research Assistant}}{November 2022 - }
  \resumeItemListStart
    \resumeItem{Audio processing for the analysis of depression in speech working on signal processing and deep audio modelling, with a particular focus on audio spectogram transformers.}
    \resumeItem{Working in an end-to-end research group that is building a custom depression corpus in the Malaysian context with multimodal visual and audio data.}
    \resumeItem{Engineered custom data processing scripts and loaders for batch operations on large audio files}
    \resumeItem{Modelling and training on SLURM high-performance clusters (Monash Monarch)}
  \resumeItemListEnd

  \resumeSubheading
  {Multimedia University}{Cyberjaya, MY}
  {\textit{Research Assistant}}{August 2022 - January 2023}
  \resumeItemListStart
    \resumeItem{Context-aware emotion analysis using multistream networks}
    \resumeItem{Conducted detailed ablation studies that examined the contributions of tabular and multi-stream additions to SOTA large image models in image emotion recognition}
    \resumeItem{Wrote a conference paper that is currently under review}
  \resumeItemListEnd

  \resumeSubheading
  {AirAsia}{Kuala Lumpur, MY}
  {\textit{Data Engineering Intern (DataOps and MLOps)}}{May 2022 - Aug 2022}
  \resumeItemListStart
    \resumeItem{The data engineering team within AirAsia Superapp builds and scales our DataOps and MLOps infrastructure, feeding production data into our lake for distributed analysis and predictive modelling.}
    \resumeItem{Partnered with data analysts, data scientists, marketing, and strategy to understand data and reporting requirements, adapt BQSQL scripts in Apache Airflow pipelines to keep up with changing business demands, and implement data pipelines on distributed Kubernetes clusters for regular ETL ingestion from Navitaire, external SFTP servers, Clevertap, Firestore, MongoDB, MySQL and PostgreSQL}
    \resumeItem{Maintained lake by monitoring for structural irregularities and backfilling from production databases on CentOS and GCP Kubernetes Engine.}
    \resumeItem{Provisioned a FastAPI server on Cloud Run for the continuous deployment of internal models that are trained using VertexAI, versioned on BigQuery and stored in GCS}
    \resumeItem{Built and deployed dockerized automation scripts to federalise dashboard reporting across internal communication platforms for management and led the migration of the logging infrastructure from Eko to Google Chat.}
    \resumeItem{Shipped DAG generators to maximise productivity by allowing a 30-man team of data engineers, data scientists and non-technical analysts to provision data pipelines with ease}
  \resumeItemListEnd

  \resumeSubheading
  {Sambal SOS (\url{https://www.sambalsos.com})}{Kuala Lumpur, MY}
  {\textit{Co-Founder and Head of Engineering}}{July 2021 - Present}
  \resumeItemListStart
    \resumeItem{Malaysia's first open-source aid data crowdsourcing platform with over 30000 users, inspired by the pandemic. We went viral, scaled rapidly, and optimised the server after building the initial version in under 4 days.}
    \resumeItem{Led a team of 5 developers across all ends of the stack, defined code practices, CI/CD and Docker workflows. Wrote frontend PWA using React.js (Chakra UI), backend server using Node.js (Express.js) and PostgreSQL, with image bucket on an AWS VPS.
    Spun up production clusters and scaled on GCP for thousands of simultaneous logins. Set up a custom PostgreSQL server on multiple EC2 and DO droplets with nginx and load balancers.}
    \resumeItem{Merged over 100 PRs from the Malaysian open source community. Was featured in over 20 major publications in Malaysia and spoke on multiple prestigious forums such as BFM and Malaysia's Big Data Week.}
  \resumeItemListEnd

    \resumeSubheading
      {Fusionex Group (Research Partnership)}{Kuala Lumpur, MY}
      {\textit{Deep Learning Researcher in Natural Language Processing}}{Aug 2021 - May 2022}
      \resumeItemListStart
        \resumeItem {An industrial research project that aims to automate the adherence checking of annual reports through a novel hybrid framework, encompassing LSTMs, word-level keyword attention and linear attention transformers (Longformer and BigBird), using Pytorch and Tensorflow, with extended research into computational long content scoring for the processing of $ \ge $ 4000-word reports.}
        \resumeItem{Collated the world's first labelled corpus of financial text from the Malaysian corporate ecosystem.}
        \resumeItem {Trained high-performance text scoring models on GCP Compute Clusters, with deployment as microservices using FastAPI and Docker \href{https://github.com/sidharrth2002/text-scoring}{\ExternalLink}.}
        \resumeItem{Defined a new avenue for multimodal natural language processing, with the introduction of the first framework to apply dual, word-level attention in tandem with neural transformers, and the first deep learning framework for the processing of text in non-academic and industrial settings.}
      \resumeItemListEnd

      \resumeSubheading
      {Rodeo}{Kuala Lumpur, MY}
      {\textit{Software Engineer (Freelance)}}{Jan 2022 - Present}
      \resumeItemListStart
        \resumeItem{Rodeo provides transit advertising solutions, and the company needed a new app that connects potential clients to marketing campaigns. As of Series B, the company has a valuation of RM 20 million.}
        \resumeItem{The engineering team at Rodeo is rebuilding the MVP from the ground up, including a real-time mobile app for drivers, an admin interface, a gamified app for the general public and a super app server.}
        \resumeItem{The super app's Dockerized server is scaled across GCP compute engines, with MongoDB clusters and GCS image buckets. Direct credit payments are automated through Touch 'n Go digital's and Stripe's API, with payment and email automation modules.}
        \resumeItem{Optical Character Recognition (OCR) and Deep Image Segmentation models are hosted on GCP Pub/Sub for the automated identity verification of drivers}
        \resumeItem{Tech Stack: Typescript, React Native, React, Node.js (Express), MongoDB, GCP}
        \resumeItemListEnd

    \resumeSubheading
      {Lava X}{Puchong, MY}
      {\textit{Software Engineer (Part Time)}}{June 2021 - Aug 2021}
      \resumeItemListStart
        \resumeItem
          {Built an MNC e-commerce CMS platform using Typescript, React (Next.js), Nest.js and GraphQL}
      \resumeItemListEnd

    \resumeSubheading
      {Auronex}{Cyberjaya, MY}
      {\textit{Software Engineer (Part Time)}}{Oct 2020 - Nov 2020}
      \resumeItemListStart
        \resumeItem
          {Integrated and deployed the frontend Flutter client and backend API for a fitness application.
          }
        \resumeItem
          {Worked on a Node.js RESTful API and a React frontend for an accounting platform and made
          custom modifications to multiple themed components for clients.
          }
      \resumeItemListEnd

  \resumeSubHeadingListEnd
  \vspace{-9pt}

  %-----------EXPERIENCE-----------------
  \section{Conference Chairmanships}

  \resumeSubHeadingListStart

    \resumeSubheading
    {The 35th Iteration of IEA AIE 2022}{Kitakyushu, Japan}
    {\textit{Session Chair}}{July 2022}
    \resumeItemListStart
      \resumeItem{Chair of Neural Networks Track}
      \resumeItem{Directed session flow and managed the Q\&A session}
    \resumeItemListEnd

  \resumeSubHeadingListEnd

  %-----------EXPERIENCE-----------------
\section{Notable Projects}
\resumeSubHeadingListStart
% \resumeItemWithHeading{Sambal SOS}{Malaysia's first open-source aid data crowdsourcing platform with over 30000 users, inspired by the pandemic. Led a team of 5 developers across all ends of the stack, defined code practices, CI/CD and Docker workflows. Merged over 100 PRs from the Malaysian open source community. Was featured in over 20 major publications in Malaysia and spoke on multiple prestigious forums. | \textit{React.js (Redux, Chakra UI), Node.js (Express), PostgreSQL, GCP} | \href{https://github.com/sidharrth2002/sambal-sos-app}{sambalsos.com}}
\resumeSubItem{Vending.js \href{https://github.com/sidharrth2002/vending.js}{\ExternalLink}}
    {PWA that automatically routes technicians to nearest appointments based on current and past locations for efficient dispatch | \textit{React.js, Node.js (Express.js), MongoDB}}
\resumeSubItem{Common Sans \href{https://github.com/sidharrth2002/common-sans}{\ExternalLink}}
    {Credit profile analysis engine powered by web scrapers and NLP using social media and e-commerce review data with support for Manglish sentiment and time-series activity | \textit{React.js, Tensorflow, Flask, Selenium}}
\resumeSubItem{Semantic Style Transfer \href{https://github.com/sidharrth2002/neural-style-transfer}{\ExternalLink}}
    {Trained and deployed pipeline that combines fast style transfer with UNet semantic segmentation for aesthetically stunning blended reproductions | \textit{Tensorflow, Pytorch, Streamlit}}
\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Technical Skills}
  \resumeSubHeadingListStart
    \resumeItem{Languages and frameworks: Python (Tensorflow, Keras, Pytorch, Scikitlearn, Pandas, Flask, OpenCV, Airflow), Javascript (Typescript, React.js, Redux, MobX, Next.js, React Native, Node.js, Express.js, Nest.js, Apollo), Dart (Flutter), Java (JavaFX), C++, HTML/CSS, PHP, MongoDB, PostgreSQL, MySQL, Redis}
    \resumeItem{CI/CD and Tools: GCP, Docker, Kubernetes}
  \resumeSubHeadingListEnd

\section{Awards}

  \resumeSubHeadingListStart
    \resumeSubItem{FWD Insurtech Regional Data Hackathon 2022}{Champion and winner of USD 5000}
    \resumeSubItem{PayHack 2023}{1st Runner Up out of 51 teams}
    \resumeSubItem{RHB Get Your Hack On 2023 ASEAN}{2nd Runner Up Out of 90+ teams}
    \resumeSubItem{RHBHack 2021}{Special Challenge Winner and Runner-up}
    \resumeSubItem{AtlasHack 2021}{Special Challenge Winner and Runner-up}
    \resumeSubItem{The Dean's List}{Faculty of Computing and Informatics MMU}
    \resumeSubItem{Crystal 1st Rank}{IGCSE Topper}
    \resumeSubItem{KUMON Mathematics Completer}{Finished KUMON Mathematics at 13, ranking 6th in the country among my age group.}
    \resumeSubItem{Duke of Edinburgh International Award (DoFE Bronze)}{International leadership program}
    \resumeSubItem{Model United Nations (MUN)}{Finished as an outstanding delegate, chairperson, and director at various MUN conferences in the Malaysian scene}
    \resumeSubItem{Merit Scholar}{Merit scholarships throughout pre-university and undergraduate years}
  \resumeSubHeadingListEnd

\section{Speaking Engagements}
  \resumeSubHeadingListStart
    \resumeSubItem{BFM.my}{Building Sambal SOS}
    \resumeSubItem{Malaysia's Big Data Week 2021}{Spoke among key Malaysian figures about using tech for community good}
    \resumeSubItem{The Center of Applied Data Science}{Malaysian Tech Changemakers}
    \resumeSubItem{Bawatana.co}{Non-profit startups}
    \resumeSubItem{The Star, Malaysiakini, Free Malaysia Today, Says.com, Varnam}{Interviews about Sambal SOS}
    \resumeSubItem{University Utara Malaysia}{Getting started in tech and software engineering}
    \resumeSubItem{University Sains Malaysia}{Tech Changemakers Panel in Varsity Hackathon 2022}
    \resumeSubItem{Universiti Sains Malaysia}{Mentor for Varsity Hackathon 2023}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \resumeItem{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
