\documentclass{article}
\usepackage{graphicx} % Required for inserting images
\usepackage{hyperref}

\title{Itemized Pointers for the Jardine Scholarship}
\author{Sidharrth Nagappan}
\date{March 2025}

\begin{document}

\maketitle

\section{Brief}

Sidharrth is an MPhil Candidate in Advanced Computer Science at the Department of Computer Science \& Technology at the University of Cambridge. He is supervised by Professor Mateja Jamnik, and Dr Nikola Simidjiewski in the Artifical Intelligence Group. Current research interests include multi-scale computational biology, multimodal reasoning and uncertainty estimation. He is a member of Magdalene College at the University of Cambridge, where he is supported by a full-ride and merit-based Jardine Scholarship. 

% No problem. Please send me your cv and itemized list of achievements organised by academic (grades, ranking, qualifications), awards, research (pubs), teaching (if any), community service (research or other). Plus if there are specific things that Jardine likes, please point out as separate category or as part of the ones I suggested above.

\section{Jardine Scholarship Selection Criteria}

Apart from academics (Sections 3, 4 \& 6), the following criteria are considered:
\begin{itemize}
    \item personal qualities and character with particular regard to the extent to
    which the applicant has demonstrated exceptional qualities of leadership
    and fellowship;
    \item community involvement and activities -- Sections 5, 6 \& 7 in this document
    \item other attributes which, in the opinion of the Scholarship Committee,
    indicate that the applicant is likely to become an outstanding citizen with
    a high commitment to the performance of public duties and/or community
    involvement -- Sections 5, 6 \& 7 in this document
\end{itemize}


\section{Education}

\begin{itemize}
    \item \textbf{University of Cambridge} - MPhil in Advanced Computer Science, 2025
    \item \textbf{Multimedia University} - B.C.S. (Hons) in Computer Science and Data Science, 2024 -- CGPA 3.99/4.00 -- \textbf{Graduated 1st/$\approx$ 250} students with the Permata Award
    \item \textbf{Politecnico di Torino} - Erasmus+ Exchange in Computer Engineering, 2023
    \item \textbf{elc International School} - IGCSE O-Levels in Mathematics, Additional Mathematics, Physics, Chemistry, Biology, English Language, English Literature, Malay Language, History, and Business Studies, 2018 -- 9A* -- \textbf{Ranked 1st in cohort}
\end{itemize}

\section{Publications}

\begin{itemize}
    \item \textbf{Sidharrth Nagappan*}, Chern Hong Lim, Anuja Thimali Dharmaratne. Towards AST-LLDs for the Analysis of Depression in Speech Signals \textit{In Proceedings of The 15th Asia Pacific Signal and Information Processing Association Annual Summit and Conference, Taipei, Taiwan}, 2023.
    \item \textbf{Sidharrth Nagappan*}, Jia Qi Tan*, Lai-Kuan Wong, John See. Context-Aware Multi-Stream Networks for Dimensional Emotion Prediction in Images \textit{In Proceedings of The 30th International Conference on Image Processing (ICIP), Kuala Lumpur, Malaysia}, 2023.
    \item \textbf{Sidharrth Nagappan*}, Hui-Ngo Goh, Amy Hui-Lan Lim. Hybrid Deep Neural Networks for Industrial Text Scoring \textit{In Proceedings of The 35th International Conference on Industrial, Engineering \& Other Applications of Applied Intelligent Systems, Kitakyushu, Japan}, 2022. -- \textbf{I served as chair of the Neural Networks track, where I regulated session flow and managed presenters.}
\end{itemize}

\section{Community}

\begin{itemize}
    \item \textbf{Co-Founder of Sambal SOS} \href{https://www.sambalsos.com/}{\textit{website}} - Malaysia's first open-source aid data crowdsourcing platform with over 30000 users, inspired by the pandemic. Led a team of 5 developers across all ends of the stack, defined code practices, CI/CD and Docker workflows. Was featured in major publications in Malaysia and spoke on multiple prestigious forums. \textit{Full Media Coverage can be found in the full academic CV (see In The News).}
\end{itemize}

\section{Professional Experience}

The full list and detailed descriptions of each role can be found in the full academic CV. I primarily worked in research \& data and platform engineering roles. Companies include:

\begin{itemize}
    \item \textbf{MoneyLion} - Software Engineer (Data Platform)
    \item \textbf{Monash University Malaysia} - Research Assistant in Affective Intelligence and Signal Processing
    \item \textbf{Multimedia University} - Research Assistant in Computational Medicine and Visual Computing
    \item \textbf{Sambal SOS} - Co-Founder
    \item \textbf{AirAsia} - Data Engineering Intern
    \item \textbf{Rodeo} - Freelance Software Engineer
    \item \textbf{Lava X \& Auronex} - Part-Time Software Engineer
\end{itemize}

\section{Awards}

\subsection{Academic}

\begin{itemize}
    \item \textbf{Jardine Scholarship} - Full-ride and merit-based scholarship for the MPhil in Advanced Computer Science at the University of Cambridge, 2024
    \item \textbf{Permata Award} - Awarded to the top student in the Faculty of Computing \& Informatics at Multimedia University, 2023
    \item \textbf{KUMON Mathematics Completer} - Completed KUMON Mathematics at the age of 13, ranking 6th in the country
\end{itemize}

\subsection{Hackathons}

\begin{itemize}
    \item \textbf{FWD Insurtech Regional Data Hackathon 2022} - Champion and winner of USD 5000
    \item \textbf{PayHack 2023} - 1st Runner Up out of 51 teams
    \item \textbf{RHB Get Your Hack On 2023 ASEAN} - 2nd Runner Up Out of 90+ teams
    \item \textbf{RHBHack 2021} - Special Challenge Winner and Runner-up
    \item \textbf{AtlasHack 2021} - Special Challenge Winner and Runner-up
\end{itemize}

\subsection{Others}

Duke of Edinburgh Bronze Award, Model United Nations Outstanding Delegate Awards \& Chairmanships

\section{Teaching, Volunteering \& Mentorship}

\begin{itemize}
    \item Lead Instructor at the Python Study Jam \& JavaScript Week 2022, Multimedia University -- \textit{Organised by the Google Developer Student Club at MMU}
    \item Hackathon Mentor at the USM Varsity Hackathon 2023 \& 2024
    \item Hackathon Mentor at the National Intervarsity Think Tank 2023
    \item Hackathon Mentor at the Google Developer Groups Georgetown DevHack 2023
    \item Community Lead at Google Developer Student Clubs MMU -- 
    \item President at Hackerspace MMU -- Ran the city's largest hacker-maker group that promotes an engineering culture within the wider student developer community, in operation for over 10 years.
    \item Head of External Outreach at IT Society -- Ran the public relations team of FCI's official student body

\end{itemize}


\end{document}
